### 2016-07-02 case-studies.tex
Edits.

\paragraph{A video view counter} The view count of a video on a
YouTube-like video-sharing website must never appear to be decreasing,
although it may not necessarily reflect the actual number of views.
We call this the monotonicity invariant of the counter. To understand
whether a straightforward implementation of the view counter preserves
the monotonicity invariant, we considered a \txnimp program that is
representative of the counter application. In particular, we
considered four concurrent transactions that operate on a shared
counter: a reader transaction that reads the counter twice obtaining
the values $k_1$ and $k_2$, respectively, and three writer
transactions, each incrementing the counter once. If the reader
witnesses a monotonically increasing view count, then $k_2\ge k_1$. We
then instantiated our reasoning framework for an {\sc sc} store with
{\sc rc} as the default isolation level (Postgres is one such store),
with the aim of verifying the program under this instantiation.  Our
attempts were however unsuccessful owing to our inability to prove
that a writer transaction always commits a value no smaller than the
current value of the counter. This points to the existence of
anamolous executions where writers may commit a value smaller than the
current value of the counter. To understand the prevalence of such
anomalies, we implemented a view counter application in Ruby-on-Rails
using standard templates and techniques\footnote{Source code of the
applications, experiments, and the tools we developed to analyze Ruby
can be found at the following anonymized url: \url{...}}. The
application stores the video count in a Postgres database, and
supports an increment operation and a read operation on the count. In
our experiments with 16 (resp. 32) concurrent writers, readers
observed 7 (17) violations of monotonicity, in 10 rounds of operation,
thus confirming that anomalies are indeed possible.

@@

To understand the effect of changing the store consistency, we
reimplemented the counter application for Cassandra, an {\sc ec} store
(We used the \emph{shim layer} of~\cite{pldi15} to equip Cassandra
with {\sc cc} and {\sc sc} consistency levels, and {\sc rc}, {\sc
mav}, and {\sc rr} isolation levels). We then repeated our experiments
with uncommitted reads and serializable writes - a combination which
was proved to preserve monotonicity on an {\sc sc} store, but
nonetheless observed monotonicity violations. The reason for such
violations became evident as we considered an instantiation our proof
framework for an {\sc ec} store. Under this instantiation, it is
impossible to derive the \C{MonotonicVis} (\S\ref{sec:ansi-isolation})
property needed to show that successive reads in a session witness
monotonically increasing state. We were however able to derive the
property assuming either causal consistency or {\sc mav} isolation
(both supported by the shim layer). We experimented with both these
options and were able to recover the monotonicity invariant.

>>>>

\paragraph{A video view counter} The view count of a video on a
YouTube-like video-sharing website must never appear to be decreasing,
although it may not necessarily reflect the actual number of views.
We call this the monotonicity invariant. To understand whether a
straightforward implementation of the view counter preserves the
invariant, we considered a \txnimp program that is representative of
the counter application. In particular, we considered four concurrent
transactions that operate on a shared counter: a reader transaction
that reads the counter twice obtaining the values $k_1$ and $k_2$,
respectively, and three writer transactions, each incrementing the
counter once. If the reader witnesses a monotonically increasing view
count, then $k_2\ge k_1$. We then instantiated our reasoning framework
for an {\sc sc} store with {\sc rc} as the default isolation level
(Postgres is one such store), with the aim of verifying the program
under this instantiation.  Our attempts were however unsuccessful
owing to our inability to prove that a writer transaction always
commits a value no smaller than the current value of the counter. This
points to the existence of anamolous executions where writers may
commit a value smaller than the current value of the counter. To
understand the prevalence of such anomalies, we implemented a view
counter application in Ruby-on-Rails using standard templates and
techniques\footnote{Source code of the applications, experiments, and
the tools we developed to analyze Ruby can be found at the following
anonymized url: \url{...}}. The application stores the video count in
a Postgres database, and supports an increment operation and a read
operation on the count. In our experiments with 16 (resp. 32)
concurrent writers, readers observed 7 (17) violations of
monotonicity, in 10 rounds of operation, thus confirming that
anomalies are indeed possible.

@@

To understand the effect of changing the store consistency, we
reimplemented the counter application for Cassandra, an {\sc ec} store
(We used the \emph{shim layer} of~\cite{pldi15} to equip Cassandra
with {\sc cc} and {\sc sc} consistency levels, and {\sc rc}, {\sc
mav}, and {\sc rr} isolation levels). We then repeated our experiments
with uncommitted reads and serializable writes - a combination which
was proved to preserve monotonicity on an {\sc sc} store, but
nonetheless observed monotonicity violations. The reason for such
violations became evident as we considered an instantiation our proof
framework for an {\sc ec} store. Under this instantiation, it is
impossible to derive the \C{MonotonicVis} (\S\ref{sec:ansi-isolation})
property needed to show that successive reads in a session witness
monotonically increasing state. We were however able to derive the
property assuming either causal consistency or {\sc mav} isolation
(both supported by the shim layer). We experimented with both these
options and were able to recover the invariant.
